Pillar 2 - Topic Modeling

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
typo in test likelihood

rm(d_AoD, d_assessment, d_ILO)
```
# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```

@@

###log_likelihood
```{r log likelihood, eval = TRUE}
# #my_loglikelihood function
# my_loglike <- function(model){
#   return(model@loglikelihood)
# }
# 
# #get loglikelihood
# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))

#Log likelihood:
test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                               logLik_manual   = map(.x = TM_manual,   .f = logLik))

@@

###Plots
```{r perplexity plots, eval = TRUE}
#perplexity
plot(topic_test$n_topic, topic_test$perplex_overview)
plot(topic_test$n_topic, topic_test$perplex_manual)

#log likelihood
plot(test3$n_topic, test3$logLik_overview)
plot(test3$n_topic, test3$logLik_manual)
```

@@

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
##Saving filed for different sessions
```{r saving, eval = TRUE}
save(topic_model_gb, 
     file = "Output/topic_model_gb.RDATA")
```
#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

@@

```
##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics, eval = FALSE}

>>>>

rm(d_AoD, d_assessment, d_ILO, list_AoD_assessment)
```
# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```
#DELETE LATERRRRRR- HELPER IMPORT
```{r}
load("Output/topic_model.RDATA")
```

@@

###log_likelihood
```{r log likelihood, eval = TRUE}
#Log likelihood:
test_likelihood <- topic_model %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                                         logLik_manual   = map(.x = TM_manual,   .f = logLik))

@@

###Plots
```{r perplexity plots, eval = TRUE}
#perplexity
plot(test_perplexity$n_topic, test_perplexity$perplex_overview)
plot(test_perplexity$n_topic, test_perplexity$perplex_manual)

#log likelihood
plot(test_likelihood$n_topic, test_likelihood$logLik_overview)
plot(test_likelihood$n_topic, test_likelihood$logLik_manual)
```

@@

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
##Saving filed for different sessions
For internal use:
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" )
```
For different sessions:
```{r saving, eval = TRUE}
save(topic_model_gb, 
     file = "Output/topic_model_gb.RDATA")
```
#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

@@

```
##Inspect topics
```{r inspect topics, eval = FALSE}
